\vspace{-2.9em}
\begin{rubric}{Education}
	\entry*[2024 -- present] 
	\textbf{Ph.D. in Computer Science} at University of Milano-Bicocca
	
	\begin{list}{\scriptsize$\bullet$}{%
		\setlength{\leftmargin}{1em}
		\setlength{\itemsep}{0em}
		\setlength{\topsep}{0em}
		\setlength{\parsep}{0em}
		\setlength{\partopsep}{0em}
	}
		\item Research on Function-as-a-Service architectures, edge computing, load balancing, reinforcement learning, and distributed systems.
		\item Supervise several B.Sc. and M.Sc. theses and manage the laboratory's server infrastructure.
	\end{list}
	
	\entry*[2021 -- 2024] 
	\textbf{M.Sc. in Computer Science} at University of Milano-Bicocca (110/110 cum laude)
	
	\begin{list}{\scriptsize$\bullet$}{%
		\setlength{\leftmargin}{1em}
		\setlength{\itemsep}{0em}
		\setlength{\topsep}{0em}
		\setlength{\parsep}{0em}
		\setlength{\partopsep}{0em}
	}
		\item Thesis: \emph{Multi-Agent Reinforcement Learning for Workload Distribution in FaaS Edge Computing Systems}.
		\item Modeled and implemented a RL environment, and conducted experiments with multi-agent decentralized RL algorithms, including PPO and SAC.
	\end{list}
	
	\entry*[2017 -- 2021] 
	\textbf{B.Sc. in Computer Science} at Sapienza University of Rome (110/110 cum laude)
	
	\begin{list}{\scriptsize$\bullet$}{%
			\setlength{\leftmargin}{1em}
			\setlength{\itemsep}{0em}
			\setlength{\topsep}{0em}
			\setlength{\parsep}{0em}
			\setlength{\partopsep}{0em}
		}
		\item Thesis: \emph{Design and Development of APIs in Go for a Domain-Specific Messaging System on SeismoCloud}.
		\item Gained hands-on experience in test-driven development, network protocols, and requirements specification in a collaborative team environment.
	\end{list}
\end{rubric}