\begin{rubric}{Work Experience}
 	\entry*[2023 -- Present] \textbf{Adjunct professor} of ``Distributed Systems'' course, B.Sc. Computer Science at University of Milano-Bicocca.
 	
 	\begin{list}{\scriptsize$\bullet$}{%
 			\setlength{\leftmargin}{1em}    % distance from left
 			\setlength{\itemsep}{0em}       % space between items
 			\setlength{\topsep}{0em}        % space above the list
 			\setlength{\parsep}{0em}        % space between paragraphs
 			\setlength{\partopsep}{0em}
 		}
		\item Delivered laboratory lectures on distributed architectures, network protocols, and concurrency models.
 		\item Covered TCP/UDP socket programming, multithreading, and concurrent design patterns in Java, RESTful backend services (Servlet-based and JAX-RS) and frontend development using plain JavaScript.
 		\item Developed assignments and supervised student projects.
 	\end{list}
 	
	\entry*[2024 -- Present] \textbf{Laboratory Tutor} of ``Distributed Systems'' course, B.Sc. Computer Science at University of Milano-Bicocca.
	%
	\entry*[Oct. -- Nov. 2025] \textbf{Corporate Instructor} for Intré Srl.
	
	\begin{list}{\scriptsize$\bullet$}{%
		\setlength{\leftmargin}{1em}    % distance from left
		\setlength{\itemsep}{0em}       % space between items
		\setlength{\topsep}{0em}        % space above the list
		\setlength{\parsep}{0em}        % space between paragraphs
		\setlength{\partopsep}{0em}
	}
		\item Designed and structured course syllabus on distributed systems and modern network protocols.
		\item Delivered training on network protocols (UDP, TCP, DNS, HTTP, QUIC, HTTP 0.9--3.0), concurrent programming, remote procedure call (with gRPC).
	\end{list}
    %
    \entry*[June -- July 2016] \textbf{Student Intern} at INFN National Laboratory of Frascati (LNF).

	\begin{list}{\scriptsize$\bullet$}{%
		\setlength{\leftmargin}{1em}    % distance from left
		\setlength{\itemsep}{0em}       % space between items
		\setlength{\topsep}{0em}        % space above the list
		\setlength{\parsep}{0em}        % space between paragraphs
		\setlength{\partopsep}{0em}
	}
    	\item Studied C programming and performed UNIX system administration tasks on AIX servers.
    	\item Explored processor architectures, server management, and operating systems used in high-performance computing.
    	\item Analyzed data storage techniques, coding methods, and information theory applied in the KLOE particle accelerator.
    \end{list}
\end{rubric}