\begin{rubric}{Volunteering Experience}
    \entry*[2015 -- present] \textbf{Open Source Contributor} (Worldwide/Online). Volunteering in a variety of open source projects, contributing to all aspects of software engineering: development, design, documentation, testing, bug hunting/fixing and localisation. Contributions to projects ranging from small scale and diffusion to larger ones like:

    \begin{itemize}
        \item Xfce (desktop environment for Linux),
        \item DevelopersItalia (official Italian hub for software in public administration),
        \item Raylib (low-level graphics library in C),
        \item Fedora (a Linux operating system).
    \end{itemize}

    Keywords: Teamwork, software engineering and development, programming languages.

    \entry*[2022 -- present] \textbf{PCOfficina} (Milan). A recognized association that aims to reduce the amount of computer waste generated, by the reuse and redistribution of computers to educational institutions and other nonprofit organizations. The association also aims to educate users about the responsible use of hardware and software.

    \smallskip

    Keywords: Team work, Public relations, Cooperation, Hardware and software skills, Public speaking, Event management, Work management, Computer regeneration.

    \entry*[2019 -- 2021] \textbf{SapienzaHub} (Rome). A group of students with the aim of facilitating the access to information about lectures, materials and exams of several courses during the bachelor's degree in Computer Science. Some projects consist of a website, a web archive, moderation for social groups and a bot software to support this.

    \smallskip

    Keywords: Social moderation, Cooperation, Communication, Web Development, Bot development.

    \entry*[2022 -- present] \textbf{Mater Amabilis and Saint Anne Pastoral Community} (Milan). Educator role in a team to manage and organize a teenager group in a year course.

    \smallskip

    Keywords: Teamwork, Event preparation and planning, Social skills.
\end{rubric}